Poseidon Adventure

### 2019-05-15 docs/index.Rmd
add maxbin testing

@@

>>>>

May 15: Changes to `atlantisom::calc_age2length` to allow user specified max length bin seem to work. Also listed under [Length compositions].

@@

Test new user specified max length bin for a large species:

<a href="https://sgaichas.github.io/poseidon-dev/TestBiggerMaxLen.html" target="_blank">Default 150 cm, try different max - May 15, 2019</a>
